\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-18 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating proof in the appendix

\section{Proximal Algorithm}\label{sec:ProxAlgo}
Following \cite{caluya2019TAC}, our idea to  \eqref{KineticProx} is to recursively update probability-weighted scattered point cloud $\{\bm{x}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ where 
$$\bm{x}_{k}^{i}\equiv\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)^{\!\top}, \quad i=1,\hdots,N.$$

>>>>

\section{Proximal Algorithm}\label{sec:ProxAlgo}
Following \cite{caluya2019TAC}, we solve \eqref{KineticProx} by recursively updating probability-weighted scattered point cloud $\{\bm{x}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ where 
$$\bm{x}_{k}^{i}\equiv\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)^{\!\top}, \quad i=1,\hdots,N, \quad k\in\mathbb{N}.$$
Thus, $\tilde{\varrho}_{k}^{i}$ is the joint PDF at the $i$th state sample
